For submission to the Journal of Integrated Pest Management

### 2021-06-03 ofv_fife_2021.Rmd
Your response seems appropriate. In our lab we just did RT-PCR and sequencing using Kundo’s paper. I feel you should highlight that USDA reconfirmed the findings of FDACS via RT-PCR, q-PCR and HTS. Because, we sent the same tissues to Beltsville so its double confirmation.

The initial site of collection was visited two more times during 2020 to gather plants for identification of the unidentified plant pathogen. These surveys were conducted during July and August to collect more putatively infected plants, including more *Liriope* spp. as well as a new species which also belongs to the family Asparagaceae; *Aspidistra elatior* Blume, which was suspected to be infected, due to both its proximity to infected *Liriope* and its unusually chlorotic leaves (`r citef("fig_2")`). Upon collection, these new samples were sent to the Florida Department of Agriculture and Consumer Services (FDACS) for identification. 
The FDACS determined that the virus was *Orchid fleck dichorhavirus* using previously published primers and methods [@Kubo2006a; @Kubo2006b; @Kubo2009a; @Kubo2009b; @RamosGonzalez2015]. Orchid subgroup 1, OFV-Orc was identified following the methods described in @Kondo2017.

>>>>

As initial diagnostics were inconclusive, new plant samples were collected during July and August of 2020 to collect more of these putatively-infected plants with ringspot symptoms. The plants collected included *Liriope* spp. and *Ophiopogon* spp., as well as *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea). *A. elatior* was suspected to be infected, due to both its proximity to infected *Liriope* and the presence of unusually chlorotic leaves (`r citef("fig_2")`). Upon collection, the new samples were sent to the Florida Department of Agriculture and Consumer Services (FDACS) for identification.

The FDACS determined that the virus was *Orchid fleck dichorhavirus* using RT-PCR and Sanger sequencing using previously published primers and methods [@Kubo2006a; @Kubo2006b; @Kubo2009a; @Kubo2009b; @RamosGonzalez2015]. Orchid subgroup 1, OFV-Orc was identified following the methods described in @Kondo2017.

I feel you should highlight that USDA reconfirmed the findings of FDACS via RT-PCR, q-PCR and HTS. Because, we sent the same tissues to Beltsville so its double confirmation.
